---
title: "Test Unit Conversion Functions"
output:
  html_document:
    df_print: paged
---

# Configuration
```{r}
library(here)
source(here("src", "R", "Scripts.R"))
```


# Test converting degrees, arc minutes, and arc seconds to degrees
```{r}
DMSToDeg(24, 13, 18)
DMSToDeg(- 24, 13, 18)
DMSToDeg(13, 4, 10)
DMSToDeg(0, -5, 30)
DMSToDeg(0, 0, 30)
DMSToDeg(0, 0, -30)
```

# Test converting degrees, arc minutes, and arc seconds to degrees
```{r}
DegToDMS(0.508333)
DegToDMS(-0.508333)
DegToDMS(10.2958)
DegToDMS(13.069444)
```

# Convert decimal hours to hours, minutes, and seconds
```{r}
HourToHMS(20.352)
HourToHMS(5.7333)
HourToHMS(-1)
HourToHMS(25)
```

# Convert hours, minutes, and seconds to decimal hours.
```{r}
HMSToHour(10, 25, 11)
HMSToHour(-2, 0, 0)
HMSToHour(25, 0, 0)
```

# Convert degrees to hours
```{r}
DegToHour(156.3)
DegToHour(90)
DegToHour(180)
DegToHour(270)
DegToHour(-1)
DegToHour(361)
```

# Convert hours to degrees
```{r}
HrToDeg(10.42)
HrToDeg(6)
HrToDeg(12)
HrToDeg(18)
HrToDeg(-1)
HrToDeg(25)
```

# Convert decimal hours to degrees, arc minutes, and arc seconds.
```{r}
HrToDMS(6)
HrToDMS(12)
HrToDMS(18)
HrToDMS(18.5)
HrToDMS(-5)
HrToDMS(25)
```

# Convert decimal degrees to hours, minutes, and seconds.
```{r}
DegToHMS(-5)
DegToHMS(361)
DegToHMS(90)
DegToHMS(180)
DegToHMS(270)
DegToHMS(359)
```


